\HeaderA{getAsRisk}{Generic Function for Computation of Asymptotic Risks}{getAsRisk}
\aliasA{getAsRisk,asBias,RealRandVariable,ContNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,asBias,RealRandVariable,ContNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asBias,UnivariateDistribution,ContNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,asBias,UnivariateDistribution,ContNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asBias,UnivariateDistribution,TotalVarNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,asBias,UnivariateDistribution,TotalVarNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asCov,RealRandVariable,ContNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,asCov,RealRandVariable,ContNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asCov,UnivariateDistribution,ContNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,asCov,UnivariateDistribution,ContNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asCov,UnivariateDistribution,TotalVarNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,asCov,UnivariateDistribution,TotalVarNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asMSE,EuclRandVariable,Neighborhood,BiasType-method}{getAsRisk}{getAsRisk,asMSE,EuclRandVariable,Neighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asMSE,UnivariateDistribution,Neighborhood,BiasType-method}{getAsRisk}{getAsRisk,asMSE,UnivariateDistribution,Neighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,asSemivar,UnivariateDistribution,Neighborhood,onesidedBias-method}{getAsRisk}{getAsRisk,asSemivar,UnivariateDistribution,Neighborhood,onesidedBias.Rdash.method}
\aliasA{getAsRisk,asUnOvShoot,UnivariateDistribution,UncondNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,asUnOvShoot,UnivariateDistribution,UncondNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,trAsCov,RealRandVariable,ContNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,trAsCov,RealRandVariable,ContNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk,trAsCov,UnivariateDistribution,UncondNeighborhood,BiasType-method}{getAsRisk}{getAsRisk,trAsCov,UnivariateDistribution,UncondNeighborhood,BiasType.Rdash.method}
\aliasA{getAsRisk-methods}{getAsRisk}{getAsRisk.Rdash.methods}
\begin{Description}\relax
Generic function for the computation of asymptotic risks.
This function is rarely called directly. It is used by 
other functions.
\end{Description}
\begin{Usage}
\begin{verbatim}
getAsRisk(risk, L2deriv, neighbor, biastype, ...)

## S4 method for signature 'asMSE, UnivariateDistribution,
##   Neighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, clip, cent, stand, trafo)

## S4 method for signature 'asMSE, EuclRandVariable,
##   Neighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, clip, cent, stand, trafo)

## S4 method for signature 'asBias, UnivariateDistribution,
##   ContNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, trafo)

## S4 method for signature 'asBias, UnivariateDistribution,
##   TotalVarNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, trafo)

## S4 method for signature 'asBias, RealRandVariable,
##   ContNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, Distr, L2derivDistrSymm, trafo, 
             z.start, A.start, maxiter, tol)

## S4 method for signature 'asCov, UnivariateDistribution,
##   ContNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, clip, cent, stand)

## S4 method for signature 'asCov, UnivariateDistribution,
##   TotalVarNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, clip, cent, stand)

## S4 method for signature 'asCov, RealRandVariable,
##   ContNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, Distr, clip, cent, stand)

## S4 method for signature 'trAsCov,
##   UnivariateDistribution, UncondNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, clip, cent, stand)

## S4 method for signature 'trAsCov, RealRandVariable,
##   ContNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, Distr, clip, cent, stand)

## S4 method for signature 'asUnOvShoot,
##   UnivariateDistribution, UncondNeighborhood, BiasType':
getAsRisk(risk, L2deriv, neighbor, biastype, clip, cent, stand, trafo)

## S4 method for signature 'asSemivar,
##   UnivariateDistribution, Neighborhood, onesidedBias':
getAsRisk(risk, L2deriv, neighbor, biastype, 
    clip, cent, stand, trafo)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{risk}] object of class \code{"asRisk"}. 
\item[\code{L2deriv}] L2-derivative of some L2-differentiable family
of probability distributions. 
\item[\code{neighbor}] object of class \code{"Neighborhood"}. 
\item[\code{biastype}] object of class \code{"BiasType"}. 
\item[\code{...}] additional parameters. 
\item[\code{clip}] optimal clipping bound. 
\item[\code{cent}] optimal centering constant. 
\item[\code{stand}] standardizing matrix. 
\item[\code{trafo}] matrix: transformation of the parameter. 
\item[\code{Distr}] object of class \code{"Distribution"}. 
\item[\code{L2derivDistrSymm}] object of class \code{"DistrSymmList"}. 
\item[\code{z.start}] initial value for the centering constant. 
\item[\code{A.start}] initial value for the standardizing matrix. 
\item[\code{maxiter}] the maximum number of iterations 
\item[\code{tol}] the desired accuracy (convergence tolerance).
\end{ldescription}
\end{Arguments}
\begin{Value}
The asymptotic risk is computed.
\end{Value}
\begin{Section}{Methods}
\describe{
\item[risk = "asMSE", L2deriv = "UnivariateDistribution", neighbor = "Neighborhood", biastype = "BiasType":] computes asymptotic mean square error in methods for
function \code{getInfRobIC}. 

\item[risk = "asMSE", L2deriv = "EuclRandVariable", neighbor = "Neighborhood", biastype = "BiasType":] computes asymptotic mean square error in methods for
function \code{getInfRobIC}. 

\item[risk = "asBias", L2deriv = "UnivariateDistribution", neighbor = "ContNeighborhood", biastype = "BiasType":] computes standardized asymptotic bias in methods for function \code{getInfRobIC}. 

\item[risk = "asBias", L2deriv = "UnivariateDistribution", neighbor = "TotalVarNeighborhood", biastype = "BiasType":] computes standardized asymptotic bias in methods for function \code{getInfRobIC}. 

\item[risk = "asBias", L2deriv = "RealRandVariable", neighbor = "ContNeighborhood", biastype = "BiasType":] computes standardized asymptotic bias in methods for function \code{getInfRobIC}. 

\item[risk = "asCov", L2deriv = "UnivariateDistribution", neighbor = "ContNeighborhood", biastype = "BiasType":] computes asymptotic covariance in methods for function \code{getInfRobIC}. 

\item[risk = "asCov", L2deriv = "UnivariateDistribution", neighbor = "TotalVarNeighborhood", biastype = "BiasType":] computes asymptotic covariance in methods for function \code{getInfRobIC}. 

\item[risk = "asCov", L2deriv = "RealRandVariable", neighbor = "ContNeighborhood", biastype = "BiasType":] computes asymptotic covariance in methods for function \code{getInfRobIC}. 

\item[risk = "trAsCov", L2deriv = "UnivariateDistribution", neighbor = "UncondNeighborhood", biastype = "BiasType":] computes trace of asymptotic covariance in methods 
for function \code{getInfRobIC}. 

\item[risk = "trAsCov", L2deriv = "RealRandVariable", neighbor = "ContNeighborhood", biastype = "BiasType":] computes trace of asymptotic covariance in methods for 
function \code{getInfRobIC}. 

\item[risk = "asUnOvShoot", L2deriv = "UnivariateDistribution", neighbor = "UncondNeighborhood", biastype = "BiasType":] computes asymptotic under-/overshoot risk in methods for 
function \code{getInfRobIC}. 

\item[risk = "asSemivar", L2deriv = "UnivariateDistribution", neighbor = "Neighborhood", biastype = "onesidedBias":] computes asymptotic semivariance in methods for
function \code{getInfRobIC}. 
}
\end{Section}
\begin{Author}\relax
Matthias Kohl \email{Matthias.Kohl@stamats.de}
\end{Author}
\begin{References}\relax
Rieder, H. (1994) \emph{Robust Asymptotic Statistics}. New York: Springer.

Ruckdeschel, P. and Rieder, H. (2004) Optimal Influence Curves for
General Loss Functions. Statistics \& Decisions (submitted).

Kohl, M. (2005) \emph{Numerical Contributions to the Asymptotic Theory of Robustness}. 
Bayreuth: Dissertation.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{asRisk-class}{asRisk.Rdash.class}}
\end{SeeAlso}

