\HeaderA{getRiskIC}{Generic function for the computation of a risk for an IC}{getRiskIC}
\aliasA{getRiskIC,IC,asBias,UncondNeighborhood,L2ParamFamily-method}{getRiskIC}{getRiskIC,IC,asBias,UncondNeighborhood,L2ParamFamily.Rdash.method}
\aliasA{getRiskIC,IC,asBias,UncondNeighborhood,missing-method}{getRiskIC}{getRiskIC,IC,asBias,UncondNeighborhood,missing.Rdash.method}
\aliasA{getRiskIC,IC,asCov,missing,L2ParamFamily-method}{getRiskIC}{getRiskIC,IC,asCov,missing,L2ParamFamily.Rdash.method}
\aliasA{getRiskIC,IC,asCov,missing,missing-method}{getRiskIC}{getRiskIC,IC,asCov,missing,missing.Rdash.method}
\aliasA{getRiskIC,IC,asMSE,UncondNeighborhood,L2ParamFamily-method}{getRiskIC}{getRiskIC,IC,asMSE,UncondNeighborhood,L2ParamFamily.Rdash.method}
\aliasA{getRiskIC,IC,asMSE,UncondNeighborhood,missing-method}{getRiskIC}{getRiskIC,IC,asMSE,UncondNeighborhood,missing.Rdash.method}
\aliasA{getRiskIC,IC,fiUnOvShoot,ContNeighborhood,missing-method}{getRiskIC}{getRiskIC,IC,fiUnOvShoot,ContNeighborhood,missing.Rdash.method}
\aliasA{getRiskIC,IC,fiUnOvShoot,TotalVarNeighborhood,missing-method}{getRiskIC}{getRiskIC,IC,fiUnOvShoot,TotalVarNeighborhood,missing.Rdash.method}
\aliasA{getRiskIC,IC,trAsCov,missing,L2ParamFamily-method}{getRiskIC}{getRiskIC,IC,trAsCov,missing,L2ParamFamily.Rdash.method}
\aliasA{getRiskIC,IC,trAsCov,missing,missing-method}{getRiskIC}{getRiskIC,IC,trAsCov,missing,missing.Rdash.method}
\aliasA{getRiskIC,TotalVarIC,asUnOvShoot,UncondNeighborhood,missing-method}{getRiskIC}{getRiskIC,TotalVarIC,asUnOvShoot,UncondNeighborhood,missing.Rdash.method}
\aliasA{getRiskIC-methods}{getRiskIC}{getRiskIC.Rdash.methods}
\begin{Description}\relax
Generic function for the computation of a risk for an IC.
\end{Description}
\begin{Usage}
\begin{verbatim}
getRiskIC(IC, risk, neighbor, L2Fam, ...)

## S4 method for signature 'IC, asCov, missing, missing':
getRiskIC(IC, risk, tol = .Machine$double.eps^0.25)

## S4 method for signature 'IC, asCov, missing,
##   L2ParamFamily':
getRiskIC(IC, risk, L2Fam, tol = .Machine$double.eps^0.25)

## S4 method for signature 'IC, trAsCov, missing, missing':
getRiskIC(IC, risk, tol = .Machine$double.eps^0.25)

## S4 method for signature 'IC, trAsCov, missing,
##   L2ParamFamily':
getRiskIC(IC, risk, L2Fam, tol = .Machine$double.eps^0.25)

## S4 method for signature 'IC, asBias, UncondNeighborhood,
##   missing':
getRiskIC(IC, risk, neighbor, biastype = symmetricBias(), tol = .Machine$double.eps^0.25)

## S4 method for signature 'IC, asBias, UncondNeighborhood,
##   L2ParamFamily':
getRiskIC(IC, risk, neighbor, L2Fam, biastype = symmetricBias(), tol = .Machine$double.eps^0.25)

## S4 method for signature 'IC, asMSE, UncondNeighborhood,
##   missing':
getRiskIC(IC, risk, neighbor, biastype = symmetricBias(), tol = .Machine$double.eps^0.25)

## S4 method for signature 'IC, asMSE, UncondNeighborhood,
##   L2ParamFamily':
getRiskIC(IC, risk, neighbor, L2Fam, biastype = symmetricBias(), tol = .Machine$double.eps^0.25)

## S4 method for signature 'TotalVarIC, asUnOvShoot,
##   UncondNeighborhood, missing':
getRiskIC(IC, risk, neighbor)

## S4 method for signature 'IC, fiUnOvShoot,
##   ContNeighborhood, missing':
getRiskIC(IC, risk, neighbor, sampleSize, Algo = "A", cont = "left")

## S4 method for signature 'IC, fiUnOvShoot,
##   TotalVarNeighborhood, missing':
getRiskIC(IC, risk, neighbor, sampleSize, Algo = "A", cont = "left")
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{IC}] object of class \code{"InfluenceCurve"} 
\item[\code{risk}] object of class \code{"RiskType"}. 
\item[\code{neighbor}] object of class \code{"Neighborhood"}. 
\item[\code{L2Fam}] object of class \code{"L2ParamFamily"}. 
\item[\code{...}] additional parameters 
\item[\code{biastype}] object of class \code{"BiasType"}. 
\item[\code{tol}] the desired accuracy (convergence tolerance).
\item[\code{sampleSize}] integer: sample size. 
\item[\code{Algo}] "A" or "B". 
\item[\code{cont}] "left" or "right". 
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
To make sure that the results are valid, it is recommended
to include an additional check of the IC properties of \code{IC} 
using \code{checkIC}.
\end{Details}
\begin{Value}
The risk of an IC is computed.
\end{Value}
\begin{Section}{Methods}
\describe{
\item[IC = "IC", risk = "asCov", neighbor = "missing", L2Fam = "missing"] asymptotic covariance of \code{IC}. 

\item[IC = "IC", risk = "asCov", neighbor = "missing", L2Fam = "L2ParamFamily"] asymptotic covariance of \code{IC} under \code{L2Fam}. 

\item[IC = "IC", risk = "trAsCov", neighbor = "missing", L2Fam = "missing"] asymptotic covariance of \code{IC}. 

\item[IC = "IC", risk = "trAsCov", neighbor = "missing", L2Fam = "L2ParamFamily"] asymptotic covariance of \code{IC} under \code{L2Fam}. 

\item[IC = "IC", risk = "asBias", neighbor = "ContNeighborhood", L2Fam = "missing"] asymptotic bias of \code{IC} under convex contaminations. 

\item[IC = "IC", risk = "asBias", neighbor = "ContNeighborhood", L2Fam = "L2ParamFamily"] asymptotic bias of \code{IC} under convex contaminations and \code{L2Fam}. 

\item[IC = "IC", risk = "asBias", neighbor = "TotalVarNeighborhood", L2Fam = "missing"] asymptotic bias of \code{IC} in case of total variation neighborhoods. 

\item[IC = "IC", risk = "asBias", neighbor = "TotalVarNeighborhood", L2Fam = "L2ParamFamily"] asymptotic bias of \code{IC} under \code{L2Fam} in case of total variation 
neighborhoods. 

\item[IC = "IC", risk = "asMSE", neighbor = "UncondNeighborhood", L2Fam = "missing"] asymptotic mean square error of \code{IC}. 

\item[IC = "IC", risk = "asMSE", neighbor = "UncondNeighborhood", L2Fam = "L2ParamFamily"] asymptotic mean square error of \code{IC} under \code{L2Fam}. 

\item[IC = "TotalVarIC", risk = "asUnOvShoot", neighbor = "UncondNeighborhood", L2Fam = "missing"] asymptotic under-/overshoot risk of \code{IC}. 

\item[IC = "IC", risk = "fiUnOvShoot", neighbor = "ContNeighborhood", L2Fam = "missing"] finite-sample under-/overshoot risk of \code{IC}. 

\item[IC = "IC", risk = "fiUnOvShoot", neighbor = "TotalVarNeighborhood", L2Fam = "missing"] finite-sample under-/overshoot risk of \code{IC}. 
}
\end{Section}
\begin{Note}\relax
This generic function is still under construction.
\end{Note}
\begin{Author}\relax
Matthias Kohl \email{Matthias.Kohl@stamats.de}
\end{Author}
\begin{References}\relax
Huber, P.J. (1968) Robust Confidence Limits. Z. Wahrscheinlichkeitstheor.
Verw. Geb. \bold{10}:269--278.

Rieder, H. (1980) Estimates derived from robust tests. Ann. Stats. \bold{8}: 106--115.

Rieder, H. (1994) \emph{Robust Asymptotic Statistics}. New York: Springer.

Kohl, M. (2005) \emph{Numerical Contributions to the Asymptotic Theory of Robustness}. 
Bayreuth: Dissertation.

Ruckdeschel, P. and Kohl, M. (2005) Computation of the Finite Sample Risk 
of M-estimators on Neighborhoods.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{getRiskIC-methods}{getRiskIC.Rdash.methods}}, \code{\LinkA{InfRobModel-class}{InfRobModel.Rdash.class}}
\end{SeeAlso}

