\HeaderA{locMEstimator}{Generic function for the computation of location M estimators}{locMEstimator}
\aliasA{locMEstimator,numeric,InfluenceCurve-method}{locMEstimator}{locMEstimator,numeric,InfluenceCurve.Rdash.method}
\aliasA{locMEstimator-methods}{locMEstimator}{locMEstimator.Rdash.methods}
\begin{Description}\relax
Generic function for the computation of location M estimators.
\end{Description}
\begin{Usage}
\begin{verbatim}
locMEstimator(x, IC, ...)

## S4 method for signature 'numeric, InfluenceCurve':
locMEstimator(x, IC, eps = .Machine$double.eps^0.5)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] sample 
\item[\code{IC}] object of class \code{"InfluenceCurve"} 
\item[\code{...}] additional parameters 
\item[\code{eps}] the desired accuracy (convergence tolerance). 
\end{ldescription}
\end{Arguments}
\begin{Value}
Returns a list with component
\begin{ldescription}
\item[\code{loc}] M estimator of location 
\end{ldescription}
\end{Value}
\begin{Section}{Methods}
\describe{
\item[x = "numeric", IC = "InfluenceCurve"] univariate location. 
}
\end{Section}
\begin{Author}\relax
Matthias Kohl \email{Matthias.Kohl@stamats.de}
\end{Author}
\begin{References}\relax
Huber, P.J. (1964) Robust estimation of a location parameter. 
Ann. Math. Stat. \bold{35}: 73--101.

Rieder, H. (1994) \emph{Robust Asymptotic Statistics}. New York: Springer.

Kohl, M. (2005) \emph{Numerical Contributions to the Asymptotic Theory of Robustness}. 
Bayreuth: Dissertation.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{InfluenceCurve-class}{InfluenceCurve.Rdash.class}}
\end{SeeAlso}

